---
title       : Data Products Course Submission
subtitle    : Bagged LOESS prediction and sample size
author      : Liran Bareket
job         : 
framework   : io2012        # {io2012, html5slides, shower, dzslides, ...}
highlighter : highlight.js  # {highlight.js, prettify, highlight}
hitheme     : tomorrow      # 
widgets     : []            # {mathjax, quiz, bootstrap}
mode        : selfcontained # {standalone, draft}
---
  

## Bootstrap Aggregating (bagging)
### What is Bagging
1. Bagging resamples a set of training data multiple time.
2. A prediction algorithm is then applied to each of the training set permutations.
3. The predictions are then combined together (averaged or majority vote)

### Benefits of Bagging
1. Bagging reduced the variablity of the prediction.
2. Works best with non linear functions

---

## Resampling Simulation
- This application will simulate resampling of data
- The application allows the user to resample the data using a variable number of times.
- The purpose of the application is to show how changing the number of times we resample the data changes the prediction curve.
- The application uses Shiny and uses the slider interactive element to gather user input.

---

## Demo Chart
This is the chart used in the application, here it is demonstrated with resampling 10 times.
```{r echo=F}
library(ElemStatLearn)
data(ozone,package="ElemStatLearn")
ozone<-ozone[order(ozone$ozone),]
set.seed(71070)
samp<-10
ll<-matrix(NA,nrow=samp,ncol=155)
for(i in 1:samp){
  ss<-sample(1:dim(ozone)[1],replace=T)
  ozone0<-ozone[ss,]
  ozone0<-ozone0[order(ozone0$ozone),]
  loess0<-suppressWarnings(loess(temperature~ozone,data=ozone0,span=0.2))
  ll[i,]<-predict(loess0,newdata=data.frame(ozone=1:155))
}
```

```{r simple-plot, fig.height=6, fig.align='center', message=F, echo=T}
plot(ozone$ozone,ozone$temperature,pch=19,cex=0.5)
for(i in 1:samp){lines(1:155,ll[i,],col="grey",lwd=2)}
lines(1:155,apply(ll,2,mean),col="red",lwd=2)
```

---

## Conclusion
- This application is highly interactive
- It demonstrate the concept of Bagging
- It demonstrate the capabilities of a shiny application
- It is fun to play with entertaining and educating

